%----------------------------------------------------------------------------------------
%   DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

\documentclass[a4paper,11pt]{article}

%----------------------------------------------------------------------------------------
%   PACKAGES
%----------------------------------------------------------------------------------------

\usepackage[T1]{fontenc}
\usepackage{parskip}
\usepackage[dvipsnames]{xcolor}
\usepackage[top=0.6cm, bottom=1.5cm, left=1cm, right=1cm]{geometry}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{titlesec}

\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    breaklinks=true,
    urlcolor=black,
    linkcolor=black
}

\titleformat{\section}
{\large\bfseries\raggedright}
{}{0em}{}[\titlerule]

\titlespacing{\section}{0pt}{6pt}{6pt}

%----------------------------------------------------------------------------------------
%   BEGIN DOCUMENT
%----------------------------------------------------------------------------------------

\begin{document}

\pagestyle{empty}

%----------------------------------------------------------------------------------------
%   TITLE
%----------------------------------------------------------------------------------------

\begin{center}

{\LARGE\bfseries Mujtaba Jafri} \\[8pt]

\href{https://www.linkedin.com/in/mujtaba30/}{LinkedIn}
 $|$
\href{mailto:jafri.h@ahduni.edu.in}{jafri.h@ahduni.edu.in}
 $|$
+91-9665857777
 $|$
\href{https://github.com/MujtabaJ30}{GitHub}
 $|$
\href{https://portfolio-mujtabaj30.vercel.app/}{Portfolio}

\end{center}


%----------------------------------------------------------------------------------------
%   EDUCATION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{tabularx}{\linewidth}{@{}l X@{}}

2021 -- 2025 &
\textbf{Ahmedabad University} \\
&
B.S. (Hons.) Computer Science (4 yrs) \\

&
Relevant Coursework:
\textbf{Statistics},
\textbf{Machine Learning},
\textbf{Human Computer Interaction} \\

\end{tabularx}


%----------------------------------------------------------------------------------------
%   PROJECTS
%----------------------------------------------------------------------------------------

\section{Projects}


%----------------------------------------------------------------------------------------
%   PROJECT 3
%----------------------------------------------------------------------------------------
\textbf{Automated Invoice Exception Handling Time for Accounts Payable teams}
\hfill
\href{https://github.com/MujtabaJ30/Invoice-exception-handler}{Live Demo}

\begin{itemize}[nosep,leftmargin=1em,itemsep=7pt]

\item Scoped the problem to \textbf{7 invoice exception types} (amount mismatch, missing PO, duplicate, etc.) and used deterministic detection since finance teams need audit trails, not probabilistic guesses.

\item Designed a \textbf{human-in-the-loop} flow where the LLM drafts fix proposals with confidence scores but a person always approves; quality gates catch bad proposals before they reach the reviewer.

\item Built a learning loop where approved fixes become rules and \textbf{auto-resolve} identical exceptions, removing human review on repeat cases.

\item Shipped end-to-end MVP (detection to resolution in \textbf{3 clicks}) with a live \textbf{ROI dashboard} tracking cost-per-invoice, labor hours saved, and touchless rate.

\end{itemize}

%----------------------------------------------------------------------------------------
%   PROJECT 1
%----------------------------------------------------------------------------------------

\textbf{Unblocked Signup Drop-off and UX Friction points for Ownly food delivery app}
\hfill
\href{https://drive.google.com/drive/folders/1f7JIWPRwlcHTbto9-NhSCaKxKleOFj6i}{Project Link}

\begin{itemize}[nosep,leftmargin=1em,itemsep=7pt]

\item Mapped the full user journey across 7 touchpoints, found \textbf{6 conversion friction points}, and used ICE scoring to rank them. SSO onboarding came out on top at 8.0/10.

\item Wrote a \textbf{full PRD} for the SSO fix with user stories, acceptance criteria, and success metrics tied to registration completion rate.

\item Sketched wireframes for an ``Explore First, Geofence Later'' flow that lets users browse without GPS permissions, solving the dead-end that blocks new signups.

\item Put together an \textbf{A/B test plan} with hypothesis, control/treatment split, and sample size to validate the fix before rolling it out.

\end{itemize}

\vspace{5pt}

%----------------------------------------------------------------------------------------
%   PROJECT 2
%----------------------------------------------------------------------------------------

\textbf{Identified \$1.5M at Risk Revenue Using RFM Analysis for Olist Ecommerce website}
\hfill
\href{https://github.com/MujtabaJ30/SQL-Product-Analytics}{GitHub}

\begin{itemize}[nosep,leftmargin=1em,itemsep=7pt]

\item Analyzed 100K orders across 9 tables to segment customers and map revenue concentration. Found 25\% of customers drive 48\% of revenue, recommended a targeted reactivation campaign to recover \textbf{\$1.5M} in at-risk customer value.

\item Discovered late deliveries penalize review scores by \textbf{1.72 points} (4.29 to 2.57), with furniture categories at 13--17\% late rate. Recommended adjusting delivery estimates by category — projected 0.3--0.5 avg review score improvement.

\item Identified that 74\% of payments are credit card (25\%+ use 4+ installments) but checkout treats all methods equally. Recommended prioritizing credit card + installment UX to streamline the path used by \textbf{3 in 4 customers}.

\end{itemize}

\vspace{5pt}

%----------------------------------------------------------------------------------------
%   EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Experience}

\textbf{Machine Learning Assistant} \textemdash\ \textit{National Institute of Electronics and Information technology}
\hfill May -- Jul 2025
\begin{itemize}[nosep,leftmargin=1em,itemsep=7pt]

\item Designed and delivered a 12-week ML curriculum for 40 students; iterated on content weekly based on student feedback and project completion data, all \textbf{40} made a working project.

\end{itemize}

\vspace{5pt}


%----------------------------------------------------------------------------------------
%   SKILLS
%----------------------------------------------------------------------------------------

\section{Skills}

\begin{tabularx}{\linewidth}{@{}l X@{}}

\textbf{Product:} &
User Research, PRD, User Stories, Wireframing, Prioritization, A/B Testing \\[3pt]

\textbf{Technical:} &
SQL, Python\\[3pt]

\textbf{AI \& ML:} &
LLM Integration, AI Evaluation Metrics, RAG \\[3pt]

\textbf{Tools:} &
Figma, Excel, Mixpanel \\

\end{tabularx}


\end{document}
